---
title       : Shiny Pitch
subtitle    : Presentation for Shiny App
author      : Pablo Iocco
job         : Software Developer
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax, quiz, bootstrap]
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## What we did?

We created an app that selects a new predictor and the plot will update the axis
with the selected predictor a new regression will be calculated and ploted, and 
at the end the most important values of the regression will be display.

--- .class #id 

## Basic example
Imagine we select *Weight (1000 lbs)*

```{r echo=FALSE}
modelFit <- lm(mtcars$mpg ~ mtcars$wt)
plot(mtcars$wt, mtcars$mpg, ylab = "Miles Per Gallon", xlab = "Weight (1000 lbs)"
     ,bty = "n", pch = 16)
abline(modelFit, col = "red", lwd = 2)
```

--- .class #id 

## Regressions Coefficients
Then we show the coefficients at the bottom

```{r} 
print(paste("R Squared:", round(summary(modelFit)$r.squared, 3)))
print(paste("Intercept:",  round(modelFit$coefficients[1],3)))
print(paste("Slope:",  round(modelFit$coefficients[2],3)))
```

--- .class #id 

## Change predictor
Then we change the predictor and a new plot and coefficients appear, thats it!
```{r echo=FALSE}
modelFit <- lm(mtcars$mpg ~ mtcars$hp)
plot(mtcars$wt, mtcars$hp, ylab = "Miles Per Gallon", xlab = "Gross horsepower"
     ,bty = "n", pch = 16)
abline(modelFit, col = "red", lwd = 2)
```


