---
title: "Human Activity Recognition"
author: "Pablo Iocco"
date: "1/26/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Processing

## Getting the data

Download and load
```{r cache=TRUE}
download.file("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv", "pml-training.csv", method="curl")
download.file("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv", "pml-testing.csv", method="curl")

pml_training <- read.csv("pml-training.csv")
pml_testing <- read.csv("pml-testing.csv")
```

## Preprocess

Libraries needed

```{r echo=FALSE}
library(dplyr, quietly = TRUE, warn.conflicts = FALSE)
library(caret, quietly = TRUE, warn.conflicts = FALSE)
```

We dont want to deal with all NA so we eliminate that columns, because they dont provide much information,
then we keep on our testing datasets the same variables, but one since `classe` is missing.
```{r}
clean_training <- pml_training %>%
  select_if(function(x) is.numeric(x)) %>%
  select_if(function(x) all(!is.na(x))) %>%
  select(-X, -raw_timestamp_part_1, -raw_timestamp_part_2)

clean_testing <- pml_testing[ , names(pml_testing) %in% names(clean_training)]
clean_training$classe <- pml_training$classe

```

Since classe is missing in the testing dataset, we divide our training dataset,
to be able to evaluate our model.

```{r}
inTrain <- createDataPartition(y=clean_training$classe,p=0.75, list=FALSE)
testing <- clean_training[-inTrain,]
training <- clean_training[inTrain,]
```


## Model Building

Because of the computing time, we build a random forest with the 10 more relevant variables

```{r cache=TRUE}
preProc <- preProcess(training[,-54],method="pca",pcaComp = 10)
trainPC <- predict(preProc,training[,-54])
rFor <- train(x = trainPC, y = factor(training$classe),method="rf", 
                trControl = trainControl(method="cv"),number=3)
```

Now we test it against our testing and evaluate the accuracy

```{r}
  testPC <- predict(preProc, testing[,-54])
  accu <- confusionMatrix(factor(testing$classe),predict(rFor,testPC))
```

Which is:  `r accu$overall[1]`.

## Results

We take our original testing vector and we predict the classes.

```{r}
 testFinal <- predict(preProc, clean_testing)
 predict(rFor,testFinal)
```

## References

Ugulino, W.; Cardador, D.; Vega, K.; Velloso, E.; Milidiu, R.; Fuks, H. Wearable Computing: Accelerometers' Data Classification of Body Postures and Movements. Proceedings of 21st Brazilian Symposium on Artificial Intelligence. Advances in Artificial Intelligence - SBIA 2012. In: Lecture Notes in Computer Science. , pp. 52-61. Curitiba, PR: Springer Berlin / Heidelberg, 2012. ISBN 978-3-642-34458-9. DOI: 10.1007/978-3-642-34459-6_6.
Cited by 2 (Google Scholar) 
